---
title: "MATH 140 - Lab 1: Exploring, Summarizing, and Visualizing Data"
author: "Huey, Dewey and Louie"
date: "9/11/24"
output: html_document
fig_width: 5 
fig_height: 3
---

```{=html}
<style type=text/css>
body{ /* Normal  */
      font-size: 14px;
  }
h1.title {
  font-size: 20px;
  color: DarkGreen;
}
h1 { /* Header 1 */
  font-size: 20px;
  color: DarkGreen;
}
h2 { /* Header 2 */
    font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 17px;
}
blockquote {
    background: #f8f8f8;
    padding: 5px 10px;
    margin: 0 0 10px;
    font-size: 16px;
    border-left: 1px solid #aaa;
    border-bottom: 1px solid #aaa;
}
</style>
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE)
library(tidyverse)
#entering data sets
survey <- read.csv("https://mphitchman.com/stats/data/student_surveys_23_24.csv")
iris<-iris
```
# Lab 1 Objectives

In this lab we begin working in RStudio to examine data sets.  In solving the exercises below, we practice how to  

(a) import data sets into an RStudio session,
(b) determine summary statistics, 
(c) present data visually,
(d) use *R Markdown* to write a lab report, and
(e) write solutions following the  **Golden Rule of Write-ups**:  <!-- Provide context for the statistics appearing in your solutions.-->
Place statistics in context using complete sentences.  In almost every question, our goal is to learn something about a particular distribution, and our answers should reflect that.  Which answer is more interesting?  (1) The mean is 2.654763; or (2) On average, Hitchman says "cripes" about 2.6 times per class.  (Answer 2, of course, because it gives the number context.)  *Make an effort to put all your answers in context.*


# SOLUTION to Q1: #

## 1 a) (observations and variables)

### Code chunk(s)

```{r}
x = c(3,4,5,6,9)
mean(x)
```

### Written solution 

The mean of the data is 5.4. 

## 1 b) (class dread)  

### Code chunk(s) 

```{r}
#enter your code here

```

### Written solution 

type your solution here. 

## 1 c) (class heights)  

### Code chunk(s) 

```{r}
#enter your code here

```

### Written solution 

type your solution here. 

## 1 d) (haircuts and shoes)

### Code chunk(s) 

```{r}
#enter your code here

```

### Written solution 

type your solution here. 

## 1 e) (degree) 

### Code chunk(s) 

```{r}
#enter your code here

```

### Written solution 

type your solution here. 

## 1 f) (degree and achievement) 

### Code chunk(s) 

```{r}
#enter your code here

```

### Written solution 

type your solution here. 

## 1 g) (height and degree) 

### Code chunk(s) 

```{r}
#enter your code here

```

### Written solution 

type your solution here. 

## 1 h) (study hours and achievement) 

### Code chunk(s) 

```{r}
#enter your code here

```

### Written solution 

type your solution here. 


# SOLUTION to Q2: 

## 2 a) (observations and variables)

### Code chunk(s) 

```{r}
#enter your code here
```

### Written solution 

type your solution here. 

## 2 b) (categorical variables)  

### Code chunk(s) 

```{r}
#enter your code here
```

### Written solution 

type your solution here. 

## 2 c) (petal length)  

### Code chunk(s) 

```{r}
#enter your code here
```

### Written solution 

type your solution here. 

## 2 d) (petal length boxplots by species)  

### Code chunk(s) 

```{r}
#enter your code here
```

### Written solution 

type your solution here. 

## 2 e) (petal length and petal width) 

### Code chunk(s) 

```{r}
#enter your code here
```

### Written solution 

type your solution here. 

## 2 f) (petal length, petal width, and species) 

### Code chunk(s) 

```{r}
#enter your code here
```

### Written solution 

type your solution here. 

## 2 g) (predicting species) 

### Code chunk(s) 

```{r}
#enter your code here
```

### Written solution 

type your solution here. 

## 2 h) (predicting species again) 

### Code chunk(s) 

```{r}
#enter your code here
```

### Written solution 

type your solution here. 


